Capstone Movielens Report

### 2025-05-13 reports/capstone-movielens-report.draft4.Rmd
Report: teamplate applied for description of user functions.

### Regularization: Common Helper Functions
\

::: {.noteblock data-latex=""}
The full source code of the functions described below are available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
:::

@@

::: {.noteblock data-latex=""}
The full version of the code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) is available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) script.
:::
:::

@@

    tuned.result <- tuned_result$tuned.result
    # tuned.result = data.frame(RMSE, parameter.value)
    # ...
    bound.idx <- get_fine_tune.param.endpoints.idx(tuned.result)
```
:::

@@

##### Value
\
A vector containing the index of the element corresponding to the minimum `RMSE` value in a given sequence, along with the indices of its nearest neighboring elements:
```{r eval=FALSE}
  c(start = i, 
    end = j,
    best = best_RMSE.idx)
```

@@

  - **:** ; 
  - **:** .

##### Details
\

@@

@@

@@

#### []() Function {#func.1}
\

@@

@@

#### []() Function {#func.2}
\

@@

### UME Model Regularization: Support Function
\

#### `regularize.test_lambda.UM_effect.cv` Function
\

This function calculates _RMSE_ of the _UME Model_ using _5-Fold CV_ method for the given $\lambda$ parameter value:
```{r eval=FALSE}
regularize.test_lambda.UM_effect.cv <- function(lambda){
  if (is.na(lambda)) {
    stop("Function: regularize.test_lambda.UM_effect.cv
`lambda` is `NA`")
  }
  um_effect <- train_user_movie_effect.cv(lambda)
  calc_user_movie_effect_RMSE.cv(um_effect)
}
```

>>>>

### UME Model Regularization: Support Functions
\

#### [regularize.test_lambda.UM_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) Function
\

This function calculates _RMSE_ of the _UME Model_ using _5-Fold Cross Validation_ method for the given $\lambda$ parameter value:
```{r eval=FALSE}
regularize.test_lambda.UM_effect.cv <- function(lambda){
  if (is.na(lambda)) {
    stop("Function: regularize.test_lambda.UM_effect.cv
`lambda` is `NA`")
  }
  um_effect <- train_user_movie_effect.cv(lambda)
  calc_user_movie_effect_RMSE.cv(um_effect)
}
```

# Appendix

### Regularization: Common Helper Functions
\
::: {.noteblock data-latex=""}
The full source code of the functions described below are available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
:::

@@

::: {.noteblock data-latex=""}
The full version of the source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) is available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) script.
:::
:::

@@

    tuned.result <- tuned_result$tuned.result
    # tuned.result = data.frame(RMSE, parameter.value)
    # ...
    bound.idx <- get_fine_tune.param.endpoints.idx(tuned.result)
    # bounnd.idx =  c(start.index, end.index, min_RMSE.index)
```
:::

@@

##### Value
\
A vector containing the index of the element corresponding to the minimum `RMSE` value in a given sequence, along with the indices of its nearest neighboring elements:
```{r eval=FALSE}
  c(start, # interval start index
    end,   # interval end index
    best)  # index of the best `RMSE`
```

@@

##### Parameters
\
A pair of matched vectors, the first of which contains the values of the input parameters for tuning, and the second, the corresponding values of the `RMSE`.

  - **param_values:** A vector containing the values of the input parameters for tuning;; 
  - **rmses:** A vector containing values of the corresponding `Root Mean Squared Errors`..

##### Details
\
Extracts the best values from the input data and returns them as a vector containing a pair of the best _input parameter_ value and the corresponding _minimum `RMSE`_.

##### Value
\
A vector containing a pair of the best _input parameter_ value and the corresponding _minimum `RMSE`_:
```{r eval=FALSE}
c(param.best_value, best_RMSE)
```

@@

### Support Functions

#### [func.00]() Function {#func.00}
\

::: { #func.00.signature .sidebar }
##### Sugnature
\
```{r eval=FALSE}

```
:::

::: { #func.00.params .sidebar }
##### Parameters
\
  - **param1:** description; 
  - **param2:** description.

:::

::: { #func.00.details .sidebar }
##### Details
\

::: {.noteblock data-latex=""}
Note 
:::
:::

::: { #func.00.value .sidebar }
##### Value
\

:::

::: { #func.00.code .sidebar }
##### Source Code
\
The soure code of the [function]() function is shown below:
```{r eval=FALSE}

@@

::: {.noteblock data-latex=""}
The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
:::
:::

--------------------------------------------------------------------------------

#### [func]() Function {#func.01}
\

::: { #func.01.signature .sidebar }
##### Sugnature
\
```{r eval=FALSE}

```
:::

::: { #func.01.params .sidebar }
##### Parameters
\
  - **param1:** description; 
  - **param2:** description.

:::

::: { #func.01.details .sidebar }
##### Details
\

::: {.noteblock data-latex=""}
Note 
:::
:::

::: { #func.01.value .sidebar }
##### Value
\

:::

::: { #func.01.code .sidebar }
##### Source Code
\
The soure code of the [function]() function is shown below:
```{r eval=FALSE}

@@

::: {.noteblock data-latex=""}
The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
:::
:::

--------------------------------------------------------------------------------

#### [func]() Function {#func.02}
\

::: { #func.02.signature .sidebar }
##### Sugnature
\
```{r eval=FALSE}

```
:::

::: { #func.02.params .sidebar }
##### Parameters
\
  - **param1:** description; 
  - **param2:** description.

:::

::: { #func.02.details .sidebar }
##### Details
\

::: {.noteblock data-latex=""}
Note 
:::
:::

::: { #func.02.value .sidebar }
##### Value
\

:::

::: { #func.02.code .sidebar }
##### Source Code
\
The soure code of the [function]() function is shown below:
```{r eval=FALSE}

::: {.noteblock data-latex=""}
The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
:::
:::

--------------------------------------------------------------------------------

#### [func.0]() Function {#func.0}
\

::: { #func.0.signature .sidebar }
##### Sugnature
\
```{r eval=FALSE}

```
:::

::: { #func.0.params .sidebar }
##### Parameters
\
  - **param1:** description; 
  - **param2:** description.

:::

::: { #func.0.details .sidebar }
##### Details
\

::: {.noteblock data-latex=""}
Note 
:::
:::

::: { #func.0.value .sidebar }
##### Value
\

:::

::: { #func.0.code .sidebar }
##### Source Code
\
The soure code of the [function]() function is shown below:
```{r eval=FALSE}

::: {.noteblock data-latex=""}
The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
:::
:::

--------------------------------------------------------------------------------

#### [func1]() Function {#func.03}
\

::: { #func.03.signature .sidebar }
##### Sugnature
\
```{r eval=FALSE}

```
:::

::: { #func.03.params .sidebar }
##### Parameters
\
  - **param1:** description; 
  - **param2:** description.

:::

::: { #func.03.details .sidebar }
##### Details
\

::: {.noteblock data-latex=""}
Note 
:::
:::

::: { #func.03.value .sidebar }
##### Value
\

:::

::: { #func.03.code .sidebar }
##### Source Code
\
The soure code of the [function]() function is shown below:
```{r eval=FALSE}

::: {.noteblock data-latex=""}
The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
:::
:::

#### [func1]() Function {#func.1}
\

::: { #func.1.signature .sidebar }
##### Sugnature
\
```{r eval=FALSE}

```
:::

::: { #func.1.params .sidebar }
##### Parameters
\
  - **param1:** description; 
  - **param2:** description.

:::

::: { #func.1.details .sidebar }
##### Details
\

::: {.noteblock data-latex=""}
Note 
:::
:::

::: { #func.1.value .sidebar }
##### Value
\

:::

::: { #func.1.code .sidebar }
##### Source Code
\
The soure code of the [function]() function is shown below:
```{r eval=FALSE}

::: {.noteblock data-latex=""}
The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
:::
:::

--------------------------------------------------------------------------------

#### [func.2]() Function {#func.2}
\

::: { #func.2.signature .sidebar }
##### Sugnature
\
```{r eval=FALSE}

```
:::

::: { #func.2.params .sidebar }
##### Parameters
\
  - **param1:** description; 
  - **param2:** description.

:::

::: { #func.2.details .sidebar }
##### Details
\

::: {.noteblock data-latex=""}
Note 
:::
:::

::: { #func.2.value .sidebar }
##### Value
\

:::

::: { #func.2.code .sidebar }
##### Source Code
\
The soure code of the [function]() function is shown below:
```{r eval=FALSE}

::: {.noteblock data-latex=""}
The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
:::
:::

--------------------------------------------------------------------------------

--------------------------------------------------------------------------------

#### [func.3]() Function {#func.3}
\

::: { #func.3.signature .sidebar }
##### Sugnature
\
```{r eval=FALSE}

```
:::

::: { #func.3.params .sidebar }
##### Parameters
\
  - **param1:** description; 
  - **param2:** description.

:::

::: { #func.3.details .sidebar }
##### Details
\

::: {.noteblock data-latex=""}
Note 
:::
:::

::: { #func.3.value .sidebar }
##### Value
\

:::

::: { #func.3.code .sidebar }
##### Source Code
\
The soure code of the [function]() function is shown below:
```{r eval=FALSE}

::: {.noteblock data-latex=""}
The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
:::
:::

--------------------------------------------------------------------------------

#### [func.4]() Function {#func.4}
\

::: { #func.4.signature .sidebar }
##### Sugnature
\
```{r eval=FALSE}

```
:::

::: { #func.4.params .sidebar }
##### Parameters
\
  - **param1:** description; 
  - **param2:** description.

:::

::: { #func.4.details .sidebar }
##### Details
\

::: {.noteblock data-latex=""}
Note 
:::
:::

::: { #func.4.value .sidebar }
##### Value
\

:::

::: { #func.4.code .sidebar }
##### Source Code
\
The soure code of the [function]() function is shown below:
```{r eval=FALSE}

::: {.noteblock data-latex=""}
The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
:::
:::

--------------------------------------------------------------------------------

#### [func.5]() Function {#func.5}
\

::: { #func.5.signature .sidebar }
##### Sugnature
\
```{r eval=FALSE}

```
:::

::: { #func.5.params .sidebar }
##### Parameters
\
  - **param1:** description; 
  - **param2:** description.

:::

::: { #func.5.details .sidebar }
##### Details
\

::: {.noteblock data-latex=""}
Note 
:::
:::

::: { #func.5.value .sidebar }
##### Value
\

:::

::: { #func.5.code .sidebar }
##### Source Code
\
The soure code of the [function]() function is shown below:
```{r eval=FALSE}

::: {.noteblock data-latex=""}
The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
:::
:::

--------------------------------------------------------------------------------

#### [func.6]() Function {#func.6}
\

::: { #func.6.signature .sidebar }
##### Sugnature
\
```{r eval=FALSE}

```
:::

::: { #func.6.params .sidebar }
##### Parameters
\
  - **param1:** description; 
  - **param2:** description.

:::

::: { #func.6.details .sidebar }
##### Details
\

::: {.noteblock data-latex=""}
Note 
:::
:::

::: { #func.6.value .sidebar }
##### Value
\

:::

::: { #func.6.code .sidebar }
##### Source Code
\
The soure code of the [function]() function is shown below:
```{r eval=FALSE}

::: {.noteblock data-latex=""}
The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
:::
:::

--------------------------------------------------------------------------------

#### [func.7]() Function {#func.7}
\

::: { #func.7.signature .sidebar }
##### Sugnature
\
```{r eval=FALSE}

```
:::

::: { #func.7.params .sidebar }
##### Parameters
\
  - **param1:** description; 
  - **param2:** description.

:::

::: { #func.7.details .sidebar }
##### Details
\

::: {.noteblock data-latex=""}
Note 
:::
:::

::: { #func.7.value .sidebar }
##### Value
\

:::

::: { #func.7.code .sidebar }
##### Source Code
\
The soure code of the [function]() function is shown below:
```{r eval=FALSE}

::: {.noteblock data-latex=""}
The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
:::
:::

--------------------------------------------------------------------------------

#### [func.8]() Function {#func.8}
\

::: { #func.8.signature .sidebar }
##### Sugnature
\
```{r eval=FALSE}

```
:::

::: { #func.8.params .sidebar }
##### Parameters
\
  - **param1:** description; 
  - **param2:** description.

:::

::: { #func.8.details .sidebar }
##### Details
\

::: {.noteblock data-latex=""}
Note 
:::
:::

::: { #func.8.value .sidebar }
##### Value
\

:::

::: { #func.8.code .sidebar }
##### Source Code
\
The soure code of the [function]() function is shown below:
```{r eval=FALSE}

::: {.noteblock data-latex=""}
The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
:::
:::

--------------------------------------------------------------------------------

#### []() Function {#func.3-1}
\

@@

================================================================================

@@

@@
